---
title: "Week 8 R Assignment"
author: "Xingjia Wu"
output: html_document
---

1 Use the rbinom() function with probability 0.5 to simulate a string of 100 coin flips.

```{r}
coin <- rbinom(100, 1, 0.5)
```

2 Test whether there is at least seven in a row

```{r}
SevenInRow <- FALSE
count <-0
total <- 8
for (i in 1:94){
  total <- sum(coin[i:(i+6)])
  if (total == 7 | total == 0){
    count <- count + 1
  }
  total <- 8
}
if (count>0){
  SevenInRow <-TRUE
}
count
SevenInRow
```

3 Enclose the codes in a loop
```{r}
p.7inrow <- function (toss){
  count <-0
  for (i in 1:toss){
    coin <- rbinom(100, 1, 0.5)
    total <- 8
    for (i in 1:94){
      total <- sum(coin[i:(i+6)])
      if (total == 7 | total == 0){
        count <- count + 1
      }
      total <- 8
    }
  }
  pb <- count/(toss*100)
  return (pb)    
}
```
Run 100-toss, show probability
```{r}
p.7inrow(1)
```
4
Run 10 times
```{r}
p.7inrow(10)
p.7inrow(100)
p.7inrow(1000)
p.7inrow(10000)
```
The more trial, the more accurate that the probability gets close to the theoretical value. 
```{r}
system.time(p.7inrow(10))
system.time(p.7inrow(100))
system.time(p.7inrow(1000))
system.time(p.7inrow(10000))
```
I feel a little slowdown when running 1000 times. Running 10000 times took more than 5 seconds. I tested on running 100,000 times and it took 55 seconds. 